The imputation methods big test

### 2020-04-30 pd2.Rmd
added tabelka z opisem zbiorow

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r}
### TU KOD HANI BEDZIE DO WKLEJENIA

dfs <- read_all_datasets()
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

@@

```{r dataset description, message = FALSE, warning=FALSE, cache = TRUE}
### TU KOD HANI BEDZIE DO WKLEJENIA

dfs <- read_all_datasets()

ids <- lapply(dfs, function(x){x$id})
names <- lapply(dfs, function(x){x$data_name})
n_inst <- lapply(dfs, function(x){x$number_of_instances})
n_features <- lapply(dfs, function(x){x$number_of_features})
number_of_numeric_features <- lapply(dfs, function(x){x$number_of_numeric_features})
number_of_categorical_features <- lapply(dfs, function(x){x$number_of_categorical_features})
number_of_missings <- lapply(dfs, function(x){x$number_of_missings})
proc_missing <- lapply(dfs, function(x){x$number_of_missing/(x$number_of_instances * x$number_of_features)})
number_of_instances_with_missings <- lapply(dfs, function(x){x$number_of_instances_with_missings})
number_of_features_with_missings <- lapply(dfs, function(x){x$number_of_features_with_missings})

#fix wrong json
names[[10]] <- "okcupid-stem"

table <- data.frame("id" = unlist(ids), 
                    "name" = unlist(names),
                    "number_of_instances" = unlist(n_inst),
                    "number_of_features" = unlist(n_features),
                    "number_of_missing" = unlist(number_of_missings),
                    "procentage_of_missing" = round(unlist(proc_missing)*100,2))

knitr::kable(table)
```
